Exploratory data analysis

### 2023-08-08 index.qmd
added satellite time period

---
title: "Exploratory data analysis"
author: 
   - name: Marcus Beck, <mbeck@tbep.org>
institute: "Tampa Bay Estuary Program"
date: "`r Sys.Date()`"
format:
  html:
    theme: cosmo
    css: styles.css
    code-tools: 
      source: https://github.com/tbep-tech/temp-manu/index.qmd
execute:
  echo: false
  warning: false
filters:
  - lightbox

>>>>

---
title: "Exploratory data analysis"
author: 
   - name: Marcus Beck, <mbeck@tbep.org>
institute: "Tampa Bay Estuary Program"
date: "`r Sys.Date()`"
format:
  html:
    theme: cosmo
    css: styles.css
    code-tools: 
      source: https://github.com/tbep-tech/temp-manu/blob/main/index.qmd
execute:
  echo: false
  warning: false
filters:
  - lightbox
